---
title: "EDS221 Morning Activities"
format: html
editor: visual
execute:
  echo: false
  warning: false
  #error: false
  message: true
---
# Overview
The following document contains two figures generated from the `pie_crab` dataset in the `lterdatasampler` package. The first figure is a bar graph showing the relationship between carapace width and latitude. The second figure is a summary table that provides the mean carapace width, standard deviation, and count of observations for each site.


```{r}
# Setup
library(lterdatasampler)
library(tidyverse)
```

## Graph

```{r}
#| fig-cap: "A splendid graph"
# head(pie_crab)
pie_crab %>% ggplot(aes(y = size, x = latitude)) +
  geom_col()
```

## Summary Table

```{r}
library(kableExtra)
summary_table <- pie_crab %>%
  group_by(site) %>%
  summarize(mean_size = round(mean(size, na.rm = TRUE),2), std_size = round(sd(size, na.rm = TRUE), 2), n = n()) %>%
  kable(col.names = c("Site", "Mean Carapace Width (cm)", "Standard Deviation (cm)", "Count"))
summary_table
```
